SLE martingales in coset conformal field theory

### 2012-04-05 AffineLieAlgebras/SLE/paper.tex
JETP letter style applied.

\documentclass[a4paper]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{multicol}
\usepackage{color}
\usepackage{graphicx}
\usepackage{hyperref}

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}

\begin{document}
\title{SLE martingales in coset conformal field theory}
\author{Anton Nazarov}
\maketitle
\begin{abstract}
  The problem is to provide a way for the concurrent use of Scramm-Loewner evolution (SLE) and conformal field theory (CFT). Both SLE and CFT are popular instruments to study critical behavior of physical models in two dimensions, but they use different objects. While Scharmm-Loewner evolution has natural connection with lattice models and is suitable for strict proofs, it lacks computational and predictive power of conformal field theory. In order to connect two approaches we consider CFT correlation functions which are martingales with respect to SLE. We establish necessary and sufficient conditions on such observables for coset models of conformal field theory and Schramm-Loewner evolution on group manifolds and check the consistency with the  behaviour of parafermionic models.
\end{abstract}

@@

\begin{equation}
  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{i}} 
  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{\bar h_i}
  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
  \label{eq:1}
\end{equation}
We can extend the definition of $\mathcal{F}$ to the whole plane by doubling the number of fields $\phi_{i}$ \cite{cardy2004boundary,cardy1984conformal} and consider $w_{i},\bar w_{i}$ as independent variables. To simplify notation we will write $\mathcal{F}(\left\{w_{i}\right\}_{i=1}^{2N})$.

@@

d \mathcal{F}_{\mathbb{H}_{t}}= \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}=0

@@

@@

  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}}-\frac{\partial_{w_{i}}}{(w_{i}-z)^{n-1}}\right);\quad \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}};\; \tilde{\mathcal{J}}^{b}_{{-n}}=-\sum_{i}\frac{\tilde{t}^{b}_{i}}{(w_{i}-z)^{n}}

@@

@@

  <0|\varphi(\infty)\phi_{1}(w_{1})\dots\phi_{2N}(w_{2N})\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\varphi(0)|0>=0
Since the set $\{\phi_{i}\}$ consists of arbitrary primary fields we conclude that $|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\varphi(0)|0>$ is null-state. Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$. Since in coset theory

@@

\begin{array}{l}
  L_{n}=L_{n}^{\gf}-L_{n}^{\af}\\
  \left[L_{n}^{\gf},J^{a}_{m}\right]=-m J^{a}_{n+m}\\
  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=-m\tilde{J}^{b}_{n+m}\\
  \left[L_{n}^{\gf},L_{m}\right]=[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}

@@

@@

Minimal models $su(2)/u(1)$.

@@

>>>>

\documentclass{jetpl}
\twocolumn

%%% article in English
\lat

%%% declaration of a new mathematical operator
\DeclareMathOperator{\sign}{sign}

%\usepackage{amsmath,amssymb,amsthm}
%\usepackage{multicol}
%\usepackage{color}
%\usepackage{graphicx}
\usepackage{hyperref}

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
%\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

%\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}

%%% article title
\title{SLE martingales in coset conformal field theory}

%%% article title - for colontitle (at the top of the page)
\rtitle{SLE martingales in coset conformal field theory}

%%% article title - for table of contents (usualy identical with \title)
\sodtitle{SLE martingales in coset conformal field theory}

%%% author(s) ( + e-mail)

\author{Anton Nazarov$^{+*}$\/\thanks{e-mail: anton.nazarov@hep.phys.spbu.ru}}

%%% author(s) - for colontitle (at the top of the page)
\rauthor{Anton Nazarov}

%%% author(s) - for table of contents
\sodauthor{Nazarov}

%%% author's address(es)
\address{
  $^+$ Department of High-Energy and Elementary Particle Physics, 
  Faculty of Physics and\\ Chebyshev Laboratory,
  Faculty of Mathematics and Mechanics, \\ SPb State University
  198904, Saint-Petersburg, Russia}

%%% dates of submition & resubmition (if submitted once, second argument is *)
\dates{06 April 2012}{*}

%%% abstract

\abstract{
  The problem is to provide a way for the concurrent use of Scramm-Loewner evolution (SLE) and conformal field theory (CFT). Both SLE and CFT are popular instruments to study critical behavior of physical models in two dimensions, but they use different objects. While Scharmm-Loewner evolution has natural connection with lattice models and is suitable for strict proofs, it lacks computational and predictive power of conformal field theory. In order to connect two approaches we consider CFT correlation functions which are martingales with respect to SLE. We establish necessary and sufficient conditions on such observables for coset models of conformal field theory and Schramm-Loewner evolution on group manifolds and check the consistency with the  behaviour of parafermionic models.}

%%% PACS numbers
\PACS{05.50.+q, 11.25.Hf, 02.20.Sv}

\begin{document}
\maketitle

@@

\begin{multline}
  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\})_{\mathbb{H}_{t}}=\\
  =\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{i}} 
  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{\bar h_i}
  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
  \label{eq:1}
\end{multline}
We can extend the definition of $\mathcal{F}$ to the whole plane by doubling the number of fields $\phi_{i}$ \cite{cardy2004boundary,cardy1984conformal} and consider $w_{i},\bar w_{i}$ as independent variables. To simplify notation we will write $\mathcal{F}(\left\{w_{i}\right\}_{i=1}^{2N})$.

@@

\begin{multline}
d \mathcal{F}_{\mathbb{H}_{t}}=\\ \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)
\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}\\=0

@@

\end{multline}

@@

\begin{eqnarray*}
  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}}-\frac{\partial_{w_{i}}}{(w_{i}-z)^{n-1}}\right)\\ \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}};\; \tilde{\mathcal{J}}^{b}_{{-n}}=-\sum_{i}\frac{\tilde{t}^{b}_{i}}{(w_{i}-z)^{n}}
\end{eqnarray*}

@@

\begin{multline}

@@

  \left<0\left|\varphi(\infty)\phi_{1}(w_{1})\dots\phi_{2N}(w_{2N})\right.\right.\\
  \left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
\left.\varphi(0)|0\right>=0
\end{multline}
Since the set $\{\phi_{i}\}$ consists of arbitrary primary fields we conclude that 
\begin{multline}
|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
\cdot\varphi(0)|0>
\end{multline}
is null-state. Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$. Since in coset theory

@@

\begin{array}{rl}
  L_{n}=& L_{n}^{\gf}-L_{n}^{\af}\\
  \left[L_{n}^{\gf},J^{a}_{m}\right]=& -m J^{a}_{n+m}\\
  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=&-m\tilde{J}^{b}_{n+m}\\
  \left[L_{n}^{\gf},L_{m}\right]=&[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=\\
  & =(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}

@@

Relations \eqref{eq:28},\eqref{eq:21} are necessary conditions for CFT correlation functions to be SLE martingales.

@@

Minimal models $su(2)/u(1)$, $su(2)\oplus su(2)/su(2)$.

@@

Coset structure of minimal models is manifest in field theory perturbed by external magnetic field \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}. This theory is supported by experimental data \cite{coldea2010quantum}. Relation between correlation functions in coset theory and SLE observables can be a starting point for the study of domain walls in lattice models away of critical point. Schramm-Loewner evolution was applied for the description of domain walls in Ising model with external field in recent paper \cite{stevenson2011domain}, although the perturbation was not compatible with affine field theory structure.
